
\documentclass{article}
\setcounter{tocdepth}{2} % 2 = subsections
\usepackage{hyperref}
\hypersetup{bookmarksdepth=3}

\errorcontextlines 10000

%\setsecnumdepth{subsection}  % number subsections and above (default is sections and above)

% Use utf-8 encoding for foreign characters
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}


\usepackage{amsmath}       
\usepackage{amsthm}        
\usepackage{amssymb}       
\usepackage{amsfonts}
\usepackage[all]{xy}
%\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}

\usepackage{url}

%\usepackage[normalem]{ulem}  % for strikeout: \sout

\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%


\usepackage[backend=biber,maxbibnames=99, style=alphabetic]{biblatex}
\addbibresource{HPrin.bib}



%%%%%% Tikz  %%%%%%%%%%%%%
\usepackage{tikz}
\usepgflibrary{arrows.meta}

\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,draw,inner sep=2pt] (char) {#1};}}

%%%%%%%%%%%%%%%%%%%%%% Theorem Styles and Counters %%%%%%%%%%%%%%%%%%%%%%%%%%



% These all use the same "theorem" counter. 
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{algorithm}[theorem]{Algorithm}
\newtheorem{axiom}[theorem]{Axiom}
\newtheorem{criterion}[theorem]{Criterion}
%\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{wildconjecture}[theorem]{Wild Conjecture}
\newtheorem{fact}[theorem]{Fact}
\newtheorem{badtheorem}[theorem]{Generalized Splitting Principle for $n\leq 3$}

\newtheorem{definition}[theorem]{Definition}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{example}[theorem]{Example}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{question}[theorem]{Question}
\newtheorem{problem}[theorem]{Main Problem}
\newtheorem{solution}[theorem]{Solution}
\newtheorem{proposed work}[theorem]{Proposed Work}




\newtheorem{remark}[theorem]{Remark}
\newtheorem{remarks}[theorem]{Remarks}
\newtheorem{summary}[theorem]{Summary}
\newtheorem{observation}[theorem]{Observation}
\newtheorem{conclusion}[theorem]{Conclusion}
\newtheorem{acknowledgement}[theorem]{Acknowledgement}
\newtheorem{case}[theorem]{Case}
\newtheorem{claim}[theorem]{Claim}




%%%%%%%%%%%%%%%%%%%%%% End Theorem Styles and Counters %%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%% New Commands %%%%%%%%%%%%%%





\DeclareMathOperator{\codim}{codim} % codimension 
\DeclareMathOperator*{\colim}{colim}
\DeclareMathOperator*{\hocolim}{hocolim}
\DeclareMathOperator*{\CoEq}{CoEq}
\DeclareMathOperator*{\Eq}{Eq}

\def\bDelta{\mathbf \Delta}


% this makes a box with an upward diagonal slash. It is sized to match \boxtimes
\newcommand{\boxslash}{{\mathrel{
	\mathchoice{\tikz{ \draw (0,0) rectangle (6.5pt,6.5pt) -- (0,0);}} %display
		{\tikz{ \draw (0,0) rectangle (6.5pt,6.5pt) -- (0,0);}} % text
		{\tikz{ \draw (0,0) rectangle (5pt,5pt) -- (0,0);}} % script
		{\tikz{ \draw (0,0) rectangle (5pt,5pt) -- (0,0);}} % scriptscript
}}}


\newcommand{\Comment}[1]{ \textcolor{Emerald}{[#1]} }

% Letters 

\def\cA{\mathcal A}\def\cB{\mathcal B}\def\cC{\mathcal C}\def\cD{\mathcal D}
\def\cE{\mathcal E}\def\cF{\mathcal F}\def\cG{\mathcal G}\def\cH{\mathcal H}
\def\cI{\mathcal I}\def\cJ{\mathcal J}\def\cK{\mathcal K}\def\cL{\mathcal L}
\def\cM{\mathcal M}\def\cN{\mathcal N}\def\cO{\mathcal O}\def\cP{\mathcal P}
\def\cQ{\mathcal Q}\def\cR{\mathcal R}\def\cS{\mathcal S}\def\cT{\mathcal T}
\def\cU{\mathcal U}\def\cV{\mathcal V}\def\cW{\mathcal W}\def\cX{\mathcal X}
\def\cY{\mathcal Y}\def\cZ{\mathcal Z}

\def\A{\mathbb A}\def\B{\mathbb B}\def\C{\mathbb C}\def\D{\mathbb D}
\def\E{\mathbb E}\def\F{\mathbb F}\def\G{\mathbb G}\def\H{\mathbb H}
\def\I{\mathbb I}\def\J{\mathbb J}\def\K{\mathbb K}\def\L{\mathbb L}
\def\M{\mathbb M}\def\N{\mathbb N}\def\O{\mathbb O}\def\P{\mathbb P}
\def\Q{\mathbb Q}\def\R{\mathbb R}
\def\S{\mathbb S}\def\T{\mathbb T}
\def\U{\mathbb U}\def\V{\mathbb V}\def\W{\mathbb W}\def\X{\mathbb X}
\def\Y{\mathbb Y}\def\Z{\mathbb Z}


% bold math symbols (for vectors/tuples)

\newcommand*\Bell{\ensuremath{\boldsymbol\ell}}
\newcommand*\Bm{\ensuremath{\boldsymbol m}}
\newcommand*\Bn{\ensuremath{\boldsymbol n}}
\newcommand*\Bt{\ensuremath{\boldsymbol t}}
\newcommand*\BW{\ensuremath{\boldsymbol W}}
\newcommand*\Bxi{\ensuremath{\boldsymbol \xi}}
\newcommand*\BM{\ensuremath{\boldsymbol M}}
\newcommand{\xymat}[1]{\begin{align*}\xymatrix{ #1}\end{align*}}
\newcommand{\xymattal}[2]{\begin{align} \label{#1} \xymatrix{ #2}\end{align}}


%%%%%%%%%%%%%%%%%%%%%% End New Commands  %%%%%%%%%%%%%%


%%%%% Commenting Commands
\setlength{\marginparwidth}{2cm}
\definecolor{comment-color}{rgb}{0.25,0.25,0.25}	% Textcolor for comment

% Margin Comment
\newcommand{\MarCom}[1]{\marginpar{\vspace*{-20pt}\tiny\color{comment-color}{ #1}\vspace*{20pt}}}
%\newcommand{\CSPcomm}[1]{{\color{CSPcolor}{#1}}}


\begin{document}
%\frontmatter

%% Title page

\pagestyle{empty}

% first column
\begin{minipage}{0.05\textwidth}
{\hspace{0.0cm}}
%{\line(0,1){\textheight} }
\tikz{\draw (0,0) -- (0, \textheight);}
%{\hspace{0.1cm}}
\end{minipage}
%second column
\begin{minipage}{0.95\textwidth}
	\textbf{\LARGE The H-Principle}\\[1.5cm]
	%\textsc{\LARGE after Galatius-Madsen-Tillmann-Weiss}\\[0.5cm]
%\\[0pt]
	\text{\Large \emph{Christopher Schommer-Pries} } \\[1cm]
	\text{\large Lectures Notes by:}\\[0.3cm]
	\text{\large Ethan Addison, Tim Campion, Shih-Kai Chiu,}\\[0.25cm]
	\text{\large Jens Kjaer, Jacob Landgraf, Jeremy Mann,}\\[0.25cm]
	\text{\large J.D. Quigley, Hari Rau-Murthy, Taylor Sutton,}\\[0.25cm]
	\text{\large Aaron Tyrrell, Timothy Warner, and Laura Wells}
	\vspace{6cm}
	
%	% Bottom of the page
	{\large \today}
\vfill

\end{minipage}

\cleardoublepage

% Frontmatter

\subsection*{Abstract}

abstract




\clearpage
\pagestyle{plain}

\tableofcontents
%\listoffigures  
%\listoftables


%\mainmatter

\section{Introduction}

To be added by Chris at a some point in the future. 

\section{Homotopy Theory}
Let $M$ be a manifold, and let $\mathcal{F}(M)$ be some space related to the geometry of $M$, e.g., the space of Riemanian metrics on $M$ with positive sectional curvature, or the space of immersions or submersions into some fixed manifold $W$. The goal of the course is trying to understand $\mathcal{F}(M)$. This will be done by constructing some other space $\mathcal{F}^h(M)$ that is the space of sections of some fiber bundle (and therefore more amenable to homotopical methods), which also possesses a comparison map $\mathcal{F}(M)\to \mathcal{F}^h(M)$. Under certain nice conditions this map is a weak homotopy equivalence, for some class of manifolds $\{M\}$, e.g., Gromonov's theorem.

To carry out this program we have some questions that need answering:
\begin{itemize}
\item Which bundle should we take sections of?
\item How do we analyze/compute $\mathcal{F}^h(M)$?
\item How do we detect weak homotopy equivalences? 
\end{itemize} 
We will start with the last question first.

\subsection{Weak Equivalences}
Most of this section should be considered review, and can be found in more details in several other sources. When it is included here, it is because we will need to generalize some well known theorems to slightly non standard cases.

Recall that given a based space $(X,x_0)$, we can define its homotopy groups $\pi_n(X,x_0)$ by $\{\text{based maps }f:(S^n,s_0)\to (X,x_0)\}/\text{based homotopy}$, for some fixed basepoint $s_0\in S^n$. 
\begin{definition}
A based map $f:(X,x_0)\to (Y,y_0)$ is a weak homotopy equivalence if $f_*:\pi_n(X,x_0)\to \pi_n(Y,y_0)$ for all $n$.
\end{definition}
We will from now drop the base points from our notations to avoid clutter. A more complete treatment can be found in \cite{may1999concise}.

We want a different characterization of weak homotopy equivalence, which will allow us to show some locality property of the notion. Consider a commutative square of pointed spaces, and pointed maps of the form:  
\xymattal{LiftSquare}{\partial D^n \ar@{=}[r] \ar@{^{(}->}[dr]&S^{n-1} \ar[r]^\alpha  & X \ar[d]^f \\& D^n \ar[r]^\beta & Y}
One could wonder when a lift $\overline{\beta}: D^n \to X$, making the whole diagram commute, exists. This turns out to be a much stronger condition than $F$ being a weak homotopy equivalence. We instead define:
\begin{definition}
A pointed map $f:X\to Y$ is a weak equivalence if for all commuting diagrams of the form $(\ref{LiftSquare})$, there exists $\overline{\beta}:D^n\to X$ such that
\xymat{\partial D^n \ar[r]^\alpha \ar@{^{(}->}[d]& X \\ D^n \ar[ur]_{\overline{\beta}} &} commutes, and 
\xymat{& X \ar[d] \\ D^n \ar[ur]^{\overline{\beta}} \ar[r]_\beta & Y}
commutes up to homotopy relative to $\partial D^n$.
\end{definition}
\begin{lemma}
$f:X\to Y$ is a weak homotopy equivalence if and only if it is a weak equivalence.
\end{lemma}
\begin{proof}
For ease of writing up the proof let $X$ and $Y$ be connected. See \cite{may1999concise} for more details.

\emph{only if}: Assume $\alpha: S^{n-1}$, such that $f_*[\alpha]=0$ in $\pi_{n-1}Y$. That means that we have a commuting square 
\xymat{\partial D^n=S^{n-1} \ar[r]^\alpha \ar@{^{(}->}[d] & X \ar[d]^f \\ D^n \ar[r]^\beta & Y} for some $\beta$; but then the existence of a lift $\overline{\beta}$ implies that $\alpha$ is null homotopic, and hence $f_*$ is injective. To show that $f_*$ is surjective take $\beta: S^n\to Y$. We need to produce $\tilde{\beta}: S^n\to X$ such that $f_*[\tilde{\beta}]=[\beta]$. Note we have the following commuting square
\xymat{\partial D^n=S^{n-1} \ar[rrr]^{\text{const}_*} \ar@{^{(}->}[d]& & & X \ar[d]^f \\ D^n \ar[r] & D^n/\partial D^n \ar@{=}[r]&S^{n-1} \ar[r]^\beta & Y}
where $\text{const}_*$ is the map that sends everything to the basepoint. This square is clearly of the form (\ref{LiftSquare}), and therefore there is $\overline{\beta}: D^n \to X$. However, by the strict commutativity we see that $\partial D^n \hookrightarrow D^n \stackrel{\beta}{\to} X$ is constant onto the basepoint, and hence we get an induced map $\tilde{\beta}:S^n=D^n/\partial D^n \to X$. By the homotopy commutativity of the lower triangle we see that $f_*[\tilde{\beta}]=[\beta]$.

\emph{if}: Given a commuting square of the form (\ref{LiftSquare}), we want to produce a lift with the correct properties. Note $[\alpha]\in\pi_{n-1} X$ with $[f\circ \alpha]=0$ in $\pi_{n-1} Y$. Because $f_*$ is an isomorphism, we see that $[\alpha]=0$, so there exists a map $\tilde{\beta}:D^n\to X$ such that the diagram
\xymat{\partial D^n \ar@{^{(}->}[d] \ar[r]^\alpha & X \\ D^n\ar[ur]_{\tilde{\beta}}}
commutes. Unfortunately $f\circ \tilde{\beta}$ need not be homotopic to $\beta$, so we need to rectify this. By construction $\beta$ and $f\circ \tilde{\beta}$ agree along the boundry so we can glue them together to get a map $\gamma: S^{n+1}\to Y$, given by $\beta$ on the Northern hemisphere $N=D^n$, $f\circ \tilde{\beta}$ on the other, and $f\circ \alpha$ on the equator $S^n$; by assumption there is unique $[\tilde{\gamma}]\in \pi_{n+1}X$ with $f_*[\tilde{\gamma}]=[\gamma]$. So we have that $f\circ \tilde{\gamma}\simeq \gamma$, so by restricting to the equator $S^n\hookrightarrow S^{n+1}$ we get
that $f\circ \tilde{\gamma}|_{S^n}\simeq \gamma|_{S^n}= f\circ \alpha$, so by $f_*:\pi_nX \to \pi_nY$ injective $\tilde{\gamma}|_{S^n}\simeq \alpha$, pick such a homotopy $H:S^n\times I \to X$, such that $H(-,0)=\alpha$, and $H(-,1)=\tilde{\gamma}|_{S^n}$. 
So we can construct $\overline{\beta}: D^n\to X$, where when $|x|>\frac{1}{2}$ we use $H(\frac{x}{|x|}, 1-2|x|)$. When $|x| \leq \frac{1}{2}$, recall that $\gamma|_N=\beta$, and therefore we use $\tilde{\gamma}|_N(2x)$.
 It is easy to check that this satisfies the desired properties for the lift.
\end{proof}

We can now prove a locality property.
\begin{theorem} \label{Thm:LocalWeak}
Let $f:X\to Y$, and $\{Y_\alpha\}_{\alpha \in A}$ an open cover of $Y$, closed under finite intersections, s.t. for $X_\alpha:=f^{-1}(Y_\alpha)$, $f|_{X_\alpha}: X_{\alpha} \to Y_{\alpha}$ are weak equivalences for all $\alpha \in A$. Then $f$ is a weak equivalence.
\end{theorem}

Note the criterion on finite intersections is necessary, otherwise given any map $X\to Y$, the suspension would always be a homotopy equivalence $\Sigma X \to \Sigma Y$, as $\Sigma Y$ has a cover consisting of the two cones (extended slightly so they are open and overlap), which (since the map is a suspension of a map) lifts to the same cover for $\Sigma X$. But each cone is contractible, so the restriction is a weak equivalence, but the map need not be an equivalence.

\begin{proof}[Theorem \ref{Thm:LocalWeak}]
For simplicity assume that $Y$ is covered by $\{Y_1,Y_2,Y_{12}=Y_1\cap Y_2\}$. The general case follows from this by building up more complicated intersections from twofold ones. Assume we are given a diagram of shape (\ref{LiftSquare}); we need to produce a lift $\overline{\beta}$. 

We identify $D^n$ with $I^n$, where $I$ is the standard interval. Since $I^n$ is compact there is $N\in \mathbb{N}$, such that if we subdivide each copy of $I$ into subintervals of length $\frac{1}{N}$, then each subcube is entirely contained in some $Y_\alpha$ for $\alpha=1,2,12$. By assumption we will know proceed to lift each subcube first by dimension, and then by first lifting those fully contained in $Y_{12}$. If we have a point on $\partial I^n$ we already know how to lift it using $\alpha$. I will now in detail give the 0th and 1st dimensional case, the rest is left as an exercise. Assume $x\in \beta(I^n-\partial I^n)$ is the image of a corner of a subcube; then we have the following diagram:
\xymat{\partial D^0 =\emptyset \ar[r] \ar@{^{(}->}[d] & X_\alpha \ar[d]^f \\ D^0=pt \ar[r]^y & Y_\alpha }
So by assumption we have a lift $x:D^0 \to X$. We pick a path $p_y$ in $Y_\alpha$ from  $y$ to $f(x)$, which we can do because of the assumption that $f:X_\alpha \to Y_\alpha$ is a weak equivalence. Now assume that we have lifted all corners of subcubes, and let $x_0$ and $x_1$ be the lift of some $y_0$ and $y_1$, respectively, such that the preimage of $y_0$ and $y_1$ in $I^n$ is connected by an edge $e$. We now need to lift this edge. We construct a map $D^1=I \to Y$ as follows: first we do $p_{y_0}$ backwards, then $\beta|_e$, and finally $p_{y_1}$, and then rescale. This gives a path from $f(x_0)$ to $f(x_1)$, and hence the following diagram commutes
\xymat{\partial D^1 \ar@{=}[r]\ar@{^{(}->}[dr]& pt \cup pt \ar[r]^{x_0 \cup x_1}  & X_\alpha \ar[d]^f \\ & D^1=pt \ar[r]^y & Y_\alpha}
So by assumption we have a lift of this path $\overline{e}: D^1\to X$, and a choice homotopy $H_e$ from $\beta|_e$ to $f\circ \overline{e}$. We need to remember this choice of homotopy to be able to lift the 2D part of the subcubes for the same reason as we needed to remember the path for the 1D case.
\end{proof}

\subsection{Fibrations}
Another class of maps that we'll be talking about are fibrations.
\begin{definition}
A map $p:E\to B$ is a Hurewicz (Serre, respectively) fibration if for each commuting square
\xymat{A\times \lbrace 0\rbrace \ar[r] \ar@{^{(}->}[d] & E \ar[d]^p \\ A\times [0,1] \ar[r] & B} 
there exists a lift such that the following diagram commutes (strictly)
\xymat{\partial A\times \lbrace 0\rbrace \ar[r] \ar@{^{(}->}[d] & E \ar[d]^p \\ A\times [0,1] \ar[r]\ar@{.>}[ur] & B,}
where $A$ ranges over all spaces (all disks $D^n$, respectively).
\end{definition}
We say that $p$ has the \textit{right lifting property} with respect to the set of maps $\lbrace A\times \lbrace 0\rbrace\hookrightarrow A\times [0,1]\rbrace$.

\begin{example}(a Hurewicz fibration) Consider the projection map $p: B\times F\to B$. Then for any square
\xymat{A\times \lbrace 0\rbrace \ar[r]^f \ar@{^{(}->}[d] & B\times F \ar[d]^p \\ A\times [0,1] \ar[r]_g & B}
construct a lift $A \times [0,1] \to B \times F$ by sending $(a,t)\mapsto (g(a,t), P_1(f(a)))$, where $P_1: B\times F\to F$ is the projection map. This works for any space $A$, so $p : B\times F\to B$ is an example of a Hurewicz fibration. 
\end{example}

\begin{example}
Let $\mathbb{Q}_\delta$ be the rational numbers considered as a discrete space, so we have a continuous map $\mathbb{Q}_\delta\to \mathbb{Q}$. Consider the map 
$$p:E=\mathbb{Q}_\delta\times I\cup_{\mathbb{Q}_\delta\times \lbrace 0\rbrace} \mathbb{Q}\times \lbrace 0\rbrace \to B=\mathbb{Q}\times I.$$ 
Suppose we have a commutative square
\xymat{D^n\times \lbrace 0\rbrace \ar[r] \ar@{^{(}->}[d] & E=\mathbb{Q}_\delta\times I\cup_{\mathbb{Q}_\delta\times \lbrace 0\rbrace} \mathbb{Q}\times \lbrace 0\rbrace \ar[d]^p \\ D^n\times [0,1] \ar[r]^g & B=\mathbb{Q}\times I.}
Since $D^n$ is connected and $g$ is continuous, the image of $D^n$ in $\mathbb{Q}$ is a single point $q$. Therefore we can consider $g$ as a map $const \times g'$ where $g' : I\to I$, and we define a lift $D^n \times [0,1] \to E$ by taking the lift which sends $D^n$ to $q \in \mathbb{Q}_\delta$. This shows that $p$ is a Serre fibration. 
\end{example}
Note that this previous example is \textit{not} a Hurewicz fibration. To see a counter-example, consider the square
\xymat{\mathbb{Q}\times \lbrace 0\rbrace \ar[r]^f \ar@{^{(}->}[d] & E \ar[d]^p \\ \mathbb{Q}\times [0,1] \ar[r]_g & B}
No lift exists for this square, since a lift $\Q \times [0,1] \to E$ would show that $p$ is a homeomorphism, which it is not. Therefore  $p:E=\mathbb{Q}_\delta\times I\cup_{\mathbb{Q}_\delta\times \lbrace 0\rbrace} \mathbb{Q}\times \lbrace 0\rbrace \to B=\mathbb{Q}\times I$ is not a Hurewicz fibration.
\begin{example}
Replacing $\mathbb{Q}$ by $\lbrace 0 \rbrace \cup \lbrace \frac{1}{n}|n\geq 1\rbrace$ in the above example gives another example of a Serre fibration which is not a Hurewicz fibration. 
\end{example}
The following table compares the two different perspectives on spaces coming from these different notions of fibrations:\\

\begin{tabular}{|c|c|}
\hline 
\textbf{Serre picture} & \textbf{Hurewicz picture} \\ 
\hline 
weak homotopy equivalences & homotopy equivalences \\ 
\hline 
Serre fibrations & Hurewicz fibrations \\ 
\hline 
relative CW pairs & NDR pairs \\ 
\hline 
all open covers & numerable covers \\ 
\hline 
more formal and general & more geometric and point set topological \\ 
\hline 
\end{tabular} 

\begin{definition}
An open cover is numerable if it admits a subordinate partition of unity.
\end{definition}

When we're talking about infinite dimensional spaces (such as the space of all metrics with positive scalar curvature, and the other motivating examples mentioned at the beginning), it is harder to talk about partitions of unity. 

%Because of this, we want to have similar locality arguments for fibrations as we did for weak equivalences.---is this the correct motivation/direction we're going??

\begin{theorem}
Let $p:E\to B$ be a map and $\lbrace B_\alpha\rbrace$ is an open cover of $B$ (numerable open cover, respectively). Set $E_\alpha:=p^{-1}(B_\alpha)$. Suppose that $p|_{E_\alpha} : E_\alpha \to B_\alpha$ is a Serre fibration (Hurewicz fibration, respectively) for all $\alpha$. Then $p:E\to B$ is also a Serre fibration (Hurewicz fibration, respectively). 
\end{theorem}

\begin{proof}
We sketch the proof for Serre fibrations. We want to construct a lift: 
\xymat{D^n\times \lbrace 0\rbrace \ar[r] \ar@{^{(}->}[d] & E \ar[d]^p \\ D^n\times [0,1] \ar[r]^g \ar@{.>}[ur] & B}
As we did for weak equivalences (see Thm 2.4) we will inductively build this lift by lifting smaller cubes. It is actually an easier construct here, because in this case we're dealing with lifts which make the diagram commute strictly, instead of lifts up to homotopy. Since $D^n \times I$ is compact, we can subdivide the cube $D^n \times I$ into $(n+1)$-dimensional cubes so that the image of each small cube is contained in some $B_\alpha$. Since each vertex of the small cubes lands in some $B_\alpha$, we can define a lift of each vertex as in the proof of Thm 2.4. We can then lift the 1-dimensional edges of each small cube, followed by the 2-dimensional faces, and so on. Note that we implicitly assumed that the restrictions of $p$ to intersections $E_\alpha \cap E_\beta$ were fibrations; we will address this assumption after proving Theorem 2.12.
\end{proof}

\begin{corollary}
If $p:E\to B$ is a fiber bundle, then $p$ is a Hurewicz (and Serre) fibration.
\end{corollary}
\begin{proof}
If $p:E\to B$ is a fiber bundle, then it is locally trivial; i.e. locally, it looks like $B_\alpha\times F\to B_\alpha$. From Example 2.6, we know this is a Hurewicz fibration. Therefore, by Theorem 2.10 we know $p:E\to B$ is a Hurewicz fibration.
\end{proof}

\begin{theorem}
Let $\mathcal{A}$ be a collection of maps. Define $\mathcal{A}^\boxslash:=\lbrace$maps satisfying the right lifting property with respect to $\mathcal{A}\rbrace$. Then $\mathcal{A}^\boxslash$ is closed under pullbacks, retracts, and transfinite compositions. 
\end{theorem}

\begin{proof}
To see invariance under pullback, consider the following diagram where $p \in \mathcal{A}^\boxslash$, the square on the right is a pullback square, and $C \to D \in \mathcal{A}$.
\xymat{
C \ar[r] \ar[d] & E\times_B X \ar[d] \ar[r] &E\ar[d]^p\\ 
D \ar[r]\ar@{.>}[ur]\ar@{.>}[urr] & X\ar[r] & B} 
We wish to construct a lift $D \to E \times_B X$. Since $p \in \mathcal{A}^\boxslash$, there exists a lift $D \to E$ as shown. The desired lift then follows from the universal property of pullbacks.

To see invariance under compositions, consider the following diagram where $E_2 \to E_1$ and $E_1 \to B$ are in $\mathcal{A}^\boxslash$, and $C \to D \in \mathcal{A}$. 
\xymat{
C \ar[r]\ar[dd] & E_2 \ar[d]\\
 & E_{1}\ar[d]\\
D \ar[r] \ar@{.>}[ur]\ar@{.>}[uur] & B\\
}
We wish to construct a lift $D \to E_2$. We may rewrite the diagram as 
\xymat{
C \ar[r]\ar[d]^= & E_2 \ar[d]\\
C \ar[r]\ar[d] & E_{1}\ar[d]\\
D \ar[r] \ar@{.>}[ur]\ar@{.>}[uur] & B\\
}
to obtain the intermediate lift $D \to E_1$ since $E_1 \to B \in \mathcal{A}^\boxslash$. The desired lift then follows since $E_2 \to E_1 \in \mathcal{A}^\boxslash.$ The proof for transfinite compositions is similar.

To see invariance under retracts, consider the following diagram

[[we didn't do this yet]]

\end{proof}

We can now show that the assumption that the restriction to intersections was a fibration in the proof of Thm 2.10 was automatically satisfied. Indeed, we can obtain the restriction to the intersection as the pullback 
\xymat{
E_1\ar[d]_p  & p^{-1}(B_1\cap B_2)\ar[d]\ar[l]\\
B_1 & B_1\cap B_2\ar[l]
}
from which we conclude the restriction is a fibration by the previous theorem.

\printbibliography

\end{document}
